### 2014-01-30 manuscripts/dpp-msbayes/dpp-msbayes-main.tex
More work on intro of DPP ms.
Incorporating more of Adam's comments and making some other tweaks as
well.

For priors on divergence-time and demographic parameters, \msb uses continuous
uniform probability distributions
This causes  divergence models with more divergence-time parameters to
integrate over a \emph{much} greater parameter space with low likelihood yet
high prior density, resulting in small marginal likelihoods relative to models
with fewer divergence-time parameters.
Furthermore, \msb uses a discrete uniform prior over the number of divergence
events $1,2,\ldots,\npairs{}$.
Because there are many more possible divergence models for intermediate numbers
of divergence events, this imposes a prior on divergence models that strongly
disfavors such models and puts most of the prior mass on models with either
very few or very many divergence-time parameters (see Figure 5 of
\citet{Oaks2012}; for brevity we will refer to this prior as ``U-shaped'').
Given that models with many divergence-time parameters have small marginal
likelihoods due to the uniform priors on divergence-time and demographic
parameters, the U-shaped prior will strongly favor models with very
few divergence events.
As a result, even when highly informative uniform priors are used for
divergence-time and demographic parameters, \msb will often strongly support
biogeographically interesting models with a small number of divergence events
shared among the taxa when, in reality, divergences were random over broad
timescales (\citet{Oaks2012}).

@@

Following the recommendations of \citet{Oaks2012}, we modify the \msb model to
test whether alternative parameterizations and priors will improve the behavior
of the approximate-Bayesian model-choice approach.
We implement a Dirichlet-process prior (DPP) over all possible models of
divergence, and use gamma and beta probability distributions in place of
uniform priors on many of the model's parameters.
Our simulation-based analyses show that the new implementation has improved
robustness, accuracy, and power compared to the original model.
Also, our results show that both the uniform priors on demographic and
divergence-time parameters and the U-shaped prior on divergence models
contribute to the biases of \msb.
When the Oaks et al.'s \citeyear{Oaks2012} sequence data of 22 pairs of taxa
from the Philippines is reanalyzed under the new model, we find a large amount
of posterior uncertainty in the number of divergence events shared among the
taxa; a result congruent with intuition given the richness of the model
and the relatively small amount of information in the data.

>>>>

For priors on divergence-time and demographic parameters, \msb uses continuous
uniform probability distributions.
This causes divergence models with more divergence-time parameters to
integrate over a \emph{much} greater parameter space with low likelihood yet
high prior density, resulting in small marginal likelihoods relative to models
with fewer divergence-time parameters \citep{Jeffreys1939,Lindley1957}.
Given that the marginal likelihood of a model weighted by its prior is what
determines its posterior probability, this causes \msb to support models with
fewer divergence events.
Furthermore, \msb uses a discrete uniform prior over the number of divergence
events $1,2,\ldots,\npairs{}$.
Because there are many more possible divergence models for intermediate numbers
of divergence events, this imposes a prior on divergence models that strongly
disfavors such models and puts most of the prior mass on models with either
very few or very many divergence-time parameters (see Figure 5 of
\citet{Oaks2012}; for brevity we will refer to this prior as ``U-shaped'').
Given that models with many divergence events have small marginal likelihoods
due to the uniform priors on divergence-time parameters, the U-shaped prior
will effectively create a strong prior preference for models with very few
divergence events.
Recently, \citet{Oaks2012} found via simulation that \msb will often strongly
support biogeographically interesting models with a small number of divergence
events shared among the taxa, even when divergences were random over broad
timescales.
They suggested this behavior was due to the combination of uniform priors on
parameters and the U-shaped prior on divergence models.

@@

We modify the \msb model to test whether alternative parameterizations and
priors will improve the behavior of the approximate-Bayesian model-choice
approach.
We implement a Dirichlet-process prior (DPP) over all possible models of
divergence, and use gamma and beta probability distributions in place of
uniform priors on many of the model's parameters.
Our simulation-based analyses show that the new implementation has improved
robustness, accuracy, and power compared to the original model.
Also, our results confirm that both the uniform priors on demographic and
divergence-time parameters and the U-shaped prior on divergence models
contribute to the biases of \msb.
After reanalyzing sequence data of 22 pairs of taxa from the Philippines
\citep{Oaks2012} under the new model, we find a large amount of posterior
uncertainty in the number of divergence events shared among the taxa; a result
congruent with intuition given the richness of the model and the relatively
small amount of information in the data.
